A tutorial on the model-dependent analysis of neutron and X-ray reflectometry

### 2020-07-24 refl_maths/paper.tex
add mention of polarised

\section{Introduction}
The mathematical concepts that underpin reflectometry are not typically affected by whether the probing radiation is the neutron or a beam of X-rays. 
Therefore, I will discuss these agnostically and only reference a given radiation source when particularly relevant.

@@

\section{Instrumental resolution}
In the analysis process, a resolution function associated with the instrumentation the reflectometry measurement was performed on it typically introduced to the model. 
This ensures greater accuracy in the modelled reflectometry to the experiment. 
These resolution functions are non-trival to define, however, the majority of reflectometry instruments will be able to offer information about the appropriate function to use.

Here, we will briefly discuss the introduction of a simple Gaussian resolution function of given width.

@@

The analysis of a reflectometry can take advantage of contrast variation, the exact methods of which are covered in other articles \cite{schurtenberger_contrast_2002}.
However, we note here that, the phrase ``global optimisation'' is often used to describe the analysis of multiple contrasts of the same structure. 
This is where a single structural model is used for the analysis of multiple measurements, but the scattering length densities are varied based on the particular contrasts under investigation. 
This method has been used to recover the phase information in neutron reflectometry analysis \cite{majkrzak_exact_1995,majkrzak_first_2000,majkrzak_phase_2003,koutsioubas_model_2019}.
However, it is also a tool in model-dependent analysis, as it reduces the number of local minimia in the parameter space. 
Typically, a global (here meaning multiple contrasts) optimisation criteria is used, for example the average or summed likelihood across all of the different measurements and model reflectometries.

>>>>

\section{Introduction}
The mathematical concepts that underpin unpolarised reflectometry are not typically affected by whether the probing radiation is the neutron or a beam of X-rays. 
Therefore, I will discuss these agnostically and only reference a given radiation source when particularly relevant.
Additionally, this work will focus only on unpolarised, nonmagnetic reflectometry analysis. 
For those interested in polarised neutron reflectometry analysis, we suggest the early work from Majkrzak, Ankner, and Felcher \cite{majkrzak_exact_1991,majkrzak_advances_1995,ankner_polarized_1999,felcher_polarized_1999}.

@@

@@

\section{Contrast variation/resonant reflectometry}
Contrast variation is an important tools in neutron reflectometry \cite{bohm_probing_2019,clifton_self_2019}, while the use of resonant X-ray reflectometry may be utilised in the study of magnetic or ferroelectric materials \cite{kemik_resonant_2011}. 
These techniques differ significantly in the practical experimental methodology, however there is substantial overlap in their analysis. 
In theory, both methods enable the ability to measure identical structural samples with variations in the scattering lengths of the components.
